Parallel Adaptive Importance Sampling

### 2017-01-24 PAIS.tex
fixed a missing reference, removed old image files
changed AMR back to time per iteration

\begin{figure}[htb]
\centering
\subfigure[Relative error in $\mathbb{E}(X)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX"}}
\subfigure[Relative error in
$\mathbb{E}(X^2)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX2"}}\\
\subfigure[Relative error in $\mathbb{E}(X^3)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX3"}}
\subfigure[\hl{Cost of resamplers per significant figure}]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_speed"}}\\
\caption{Comparison of the performance between different resampling schemes. The example in Section~\ref{sec:problem 1} is implemented for this demonstration.}
\label{fig:AMR}
\end{figure}

To test the accuracy and speed of the three resamplers (ETPF,
bootstrap and AMR), we drew a sample of size $M$ from the proposal distribution
$\mathcal{N}(1,2)$. Importance weights were assigned, based on a
target distribution of $\mathcal{N}(2,3)$. The statistics of the
resampled outputs were compared with the original weighted samples. Figure \ref{fig:AMR} (a)-(c) show how the relative errors in the first
three moments of the samples changes with ensemble size $M$ for the three different
samplers. As expected, the AMR lies somewhere between the high
accuracy of the ETPF and the less accurate bootstrap
resampling. Note that only the error for the bootstrap multinomial
sampler is presented for the first moment since both the ETPF and the
AMR preserve the mean of the original weighted samples up to machine precision. Figure \ref{fig:AMR} \hl{(d) shows how the computational cost,
measured in seconds, scales with the ensemble size for the three
different methods}. These results demonstrate that the AMR behaves how we wish, and
importantly ensures that exactly one sample of the output will lie in
each region with weights up to $\frac{1}{M}$ of the total.

We will use the AMR in the numerics in Section \ref{sec:chem_conv}
where we have chosen to use a larger ensemble size. We do not claim
that the AMR is the optimal choice within PAIS, but it does have
favourable features, and demonstrates how different choices of
resampler can affect the speed and accuracy of the PAIS algorithm.

>>>>

\begin{figure}[htb]
\centering
\subfigure[Relative error in $\mathbb{E}(X)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX"}}
\subfigure[Relative error in
$\mathbb{E}(X^2)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX2"}}\\
\subfigure[Relative error in $\mathbb{E}(X^3)$]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_EX3"}}
\subfigure[Cost of resamplers per iteration]{\includegraphics[width=0.45\textwidth]{"figures/Resampler_speed"}}\\
\caption{Comparison of the performance between different resampling schemes. The example in Section~\ref{sec:problem 1} is implemented for this demonstration.}
\label{fig:AMR}
\end{figure}

To test the accuracy and speed of the three resamplers (ETPF,
bootstrap and AMR), we drew a sample of size $M$ from the proposal distribution
$\mathcal{N}(1,2)$. Importance weights were assigned, based on a
target distribution of $\mathcal{N}(2,3)$. The statistics of the
resampled outputs were compared with the original weighted samples. Figure \ref{fig:AMR} (a)-(c) show how the relative errors in the first
three moments of the samples changes with ensemble size $M$ for the three different
samplers. As expected, the AMR lies somewhere between the high
accuracy of the ETPF and the less accurate bootstrap
resampling. Note that only the error for the bootstrap multinomial
sampler is presented for the first moment since both the ETPF and the
AMR preserve the mean of the original weighted samples up to machine precision. Figure \ref{fig:AMR} (d) shows how the computational cost,
measured in seconds, scales with the ensemble size for the three
different methods. These results demonstrate that the AMR behaves how we wish, and
importantly ensures that exactly one sample of the output will lie in
each region with weights up to $\frac{1}{M}$ of the total.

We will use the AMR in the numerics in Section \ref{sec:mixture}
where we have chosen to use a larger ensemble size. We do not claim
that the AMR is the optimal choice within PAIS, but it does have
favourable features, and demonstrates how different choices of
resampler can affect the speed and accuracy of the PAIS algorithm.
